% cv-us.tex
% $Id: cv-us.tex,v 1.28 2006/12/12 22:53:52 jrblevin Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Richard T. Guy},
  pdfcreator={$ $Id: RGuyResume.tex,v 1.28 2006/12/12 22:53:52 rguy Exp $ $},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={}
}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{Richard T. Guy}

\begin{resume}

\begin{ncolumn}{2}
  Department of Computer Science       & Skype: richard.t.guy \\
  Bahen Center                  & {\tt guy@cs.toronto.edu} \\
  University of Toronto & {\tt http://www.cs.toronto.edu/$\sim$guy} \\
  Toronto, ON, Canada      & \\
\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf Education}
Ph.D. Student (on leave) in Computer Science, University of Toronto

M.S. Computer Science, Wake Forest University, 2010 \\
\indent Master's Thesis: {\it Machine Learning for Biostatisticians: A Hypothesis Driven Approach}

M.A. Mathematics, Wake Forest University, 2009 \\
\indent Master's Thesis: {\it Some new results on Composition-Delay Equations with Asymptotically Periodic Solutions}

B.A. Mathematics, Philosophy and Religion, Appalachian State University, 2007,
{\it Summa Cum Laude} \\ Minor: Computer Science \\
\indent Honors Thesis: {\it Diagonalization and the Liar}

%---------------------------------------------------------------------------

\section{\bf Honors and Awards}
\begin{itemize}
\item Winner of the 2009 Gordon A. Melson Outstanding Master's Student Award.
\item Winner of ``Best Poster Award" at the Graduate Research Day Poster Session, Wake Forest University, April, 2009.
\item Runner up for best poster at the Graduate Research Day Poster Session, Wake Forest University, April, 2010.
\item Uplison Pi Epsilon inductee.
\item Pi Mu Epsilon inductee.
\item Graduating Class Representative and podium speaker for May Commencement, 2007, Appalachian State University
\item Chancellor's List (GPA $>$ 3.85) every semester at Appalachian State University
\item Academic Excellence Award, 2006, 2007, Appalachian State University
\item Outstanding Senior Award, Department of Philosophy and Religion, Appalachian State University, 2006, 2007
\end{itemize}

\section{\bf Recent and Ongoing Collaborations}
\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body\\
\end{format}


\title{Urban Mobility for Visually Impaired Pedestrians}
\employer{Dr. Khai Truong}
\location{University of Toronto}
\dates{August, 2011 to present}
\begin{position}
This project investigated the information needs of visually impaired pedestrians when crossing urban intersections. Current work involves using Computer Vision to annotate an urban environment in real-time and offline settings.
\end{position}

\title{Research Assistant}
\employer{Dr. Carl Langefeld}
\location{Wake Forest University Baptist Medical College Dept. of Biostatistics}
\dates{August, 2008 to present}
\begin{position}
Developing the computational tools necessary to consider genome-wide datasets.  In particular, data mining and aggregation software utilizing online databases.
\end{position}

\title{PERIODIC}
\employer{Dr. Robert Plemmons}
\location{Wake Forest University Departments of Mathematics and Computer Science}
\dates{April 2008 to May 2009}
\begin{position}
Applied super-resolution imaging techniques to multi-lenslet imaging systems.
\end{position}

%---------------------------------------------------------------------------

\section{\bf Teaching Experience}

\begin{itemize}
\item Teaching Assistant, CSC 336 (Numerical Methods), University of Toronto, Fall 2010, 2011, Spring 2012
\item Teaching Assistant, CSC 373 (Algorithm Design and Analysis), University of Toronto, Summer 2011
\item Teaching Assistant, Math 112, Wake Forest University, Fall 2007, Spring 2008
\item Teaching Assistant, ``Utopian Societies," (Interdisciplinary Course), Appalachian State University, Fall 2005
\item Teaching Assistant, ``Generations," (Introductory History Course), Appalachian State University, Fall 2004
\end{itemize}

%------------------------------------------------------------------------------

\section{\bf Employment}
%
 \begin{format}
 \employer{l}\location{r}\\
 \title{l}\dates{r}\\
 \body\\
 \end{format}
%

 \title{Lead Data Scientist}
 \employer{Wave Accounting}
 \location{Toronto, ON}
 \dates{March 2012 to present}
 \begin{position}
 {\em Current position }
Manage Wave’s data set and data insights team. Develop analytics platform and provided actionable insight to executives. Architect and develop data-focused consumer applications.
 \end{position}

 \title{Director}
 \employer{Apps for the Greater Good}
 \location{Remote}
 \dates{January 2011 to present}
 \begin{position}
This is the organization dedicated to supporting Verbal Victor and to bringing other assistive technologies to market. I am the lead technologist for this team.
 \end{position}

 \title{Mathematical Specialist}
 \employer{Dynasoft, LLC}
 \location{Blacksburg, VA}
 \dates{2007-2009}
 \begin{position}
    Develop and test an engineering software package that performs one step Value Stream Mapping.
 \end{position}

%------------------------------------------------------------------------------

%%===========================================================================%%
%\newpage
%\opening

\section{\bf Publications (including conference publications)}

[15] R.T. Guy and K.N. Truong ``CrossingGuard: Exploring Information Content in Navigation Aids for the Visually Impaired." In the Proceedings of CHI 2012: The ACM Conference on Human Factors in Computing Systems (May 5-10, Austin, TX), 2012.

[14] D. Dearman, R.T. Guy, and K.N. Truong ``Determining the Orientation of Proximate Mobile Devices using their Back Facing Camera" In the Proceedings of CHI 1012: The ACM Conference on Human Factors in Computing Systems (May 5-10, Austin, TX), 2012.

[13] V.P. Pauca and R.T. Guy ``Mobile Apps for the Greater Good: A Socially Relevant Approach to Software Engineering" in SIGCSE '12: Proceedings of the 43th ACM technical symposium on Computer science education (March, 2012).

[12] F. Li, R.T. Guy, K. Yatani, K.N. Truong ``The 1line keyboard: a QWERTY layout in a single line" in UIST '11 Proceedings of the 24th annual ACM symposium on User interface software and technology

[11] R.T. Guy, P. Santago, C.D. Langefeld ``Bootstrap Aggregating of Alternating Decision Trees to Detect Sets of SNPs that Associate with Disease" in Genetic Epidemiology (Vol 32, Issue 2, Feb 2012). 

[10] L. Chen, Y. Guoqiang, C.D. Langefeld, D.J. Miller, R.T. Guy, X. Yuan, D. Herrington, and Y. Wang, ``Comparative Analysis of Methods for Detecting Interactive SNPs." BMC Genomics. 2011; 12: 344. 

[9] P.S. Ramos, J.T. Ziegler, M.E. Comeau, A.H. Williams, R.T. Guy, C.J. Lessard, L.A. Criswell, P.M. Gaffney, J.A. Kelly, K.M. Kaufman, R. Zidovetzki, C.O. Jacob, R.P. Kimberly, B.P. Tsao, T.J. Vyse, J.B. Harley, M.E. Alarc\'{o}n-Riquelme, C.D. Langefeld, and K.L. Moser, ``Genetic Analyses of Interferon Pathway-Related Genes Reveals Multiple New Loci Associated with Systemic Lupus Erythematosus (SLE)"  Submitted to Arthritis \& Rheumatism.

%[11] R.T. Guy, W. Wang, M. Marion, P. Ramos, T. Howard, C.D. Langefeld  ``SNPDOC: A Web Based SNP Selection Utility," submitted to BMC Bioinformatics.

%[10] A. Williams, R.T. Guy, C. Langefeld, T. Fingerlin, ``Multiple Imputation Strategies for Haplotype Association Analyses in General Pedigrees" in preparation.

[8] Q. Zhang, R.T. Guy and R.J. Plemmons, ``Matrix Structures and Parallel Algorithms for Image Superresolution Reconstruction," SIAM Journal on Matrix Analysis and Applications (Vol.31, No.4)

[7] K. S. Berenhaut, R. T. Guy and C. L. Barrett, ``Globally asymptotic behavior for minimum difference equations," accepted by the International Journal of Difference Equations.

[6] R. T. Guy, M. Misiurewicz, ``Euler Approximations Can Destroy Unbounded Solutions." PODE 2009 proceedings, a special issue of Fasciculic Mathematici.  Vol 44, No. 1 (2009).

[5] M. Mirotznik, S. Mathews, R. Plemmons, P. Pauca, T. Torgersen, R. Barnard, R.T. Guy, B. Gray, Q. Zhang, J. van der Gracht, C. Peterson, M. Bodnar, S. Prasad, ``A Practical Enhanced-Resolution Integrated Optical-Digital Imaging Camera (PERIODIC)" in Proc. SPIE Conference on Defense Security and Sensing, April, 2009.

[4] K. S. Berenhaut, R. T. Guy, ``Symmetric Functions and Difference Equations with Asymptotically Period-Two Solutions," International Journal of Difference Equations, Vol 4, No. 1. (2009)

[3] K. S. Berenhaut, R. T. Guy, ``Periodicity and boundedness for the integer solutions to a minimum-delay
difference equation," Journal of Difference Equations and Applications, Vol 16, No. 8.  (2010)

[2] K. S. Berenhaut, R. T. Guy, and N. G. Vish, ``An Optimal Bound for Inverses of Triangular Matrices with Monotone Entries," in press, Journal of Linear and Multi-linear algebra.

[1] K. S. Berenhaut, R. T. Guy, and N. G. Vish, ``A 1-norm bound for inverses of triangular matrices
with monotone entries," Banach J. Math. Anal. 2, no. 1, 112\{121\}  (2008).


%------------------------------------------------------------------------------

\section{\bf Presentations}
%
[10] ``Applications of number theory to asymptotic behavior of solutions of difference equations."  Invited Talk at Joint Mathematical Meetings in San Francisco, January, 2010.

[9] ``Some recent results on minimum-delay difference equations" Invited Talk at AMS Regional Meeting at The Pennsylvania State University on October 24, 2009.

[8] ``Periodicities in Composition-Delay Difference Equations," Progress on Difference Equations 2009, Bedlewo, Poland, May, 2009.

[7] ``Challenges and Opportunities in SNP Data Analysis," Math Club lecture, Wake Forest University, April, 2009. 

[6] ``Some new results on Composition-Delay Equations with Asymptotically Periodic Solutions" poster presented at Graduate Research Poster Session, Wake Forest University, April 2009.

[5] ``Symmetric Functions and Difference Equations with Asymptotically Period-Two Solutions" presented January, 2009, Joint Mathematics Meeting (JMM), Washington D.C.

[4] ``The periodic character of some rational difference equations of arbitrary order with truncation (Preliminary report)" presented January, 2008, JMM, San Diego, CA

[3] ``Diagonalization and the Liar" presented April of 2007 at National Conference on Undergraduate Research, Dominican University, San Raphael, CA

[2] ``A Revaluation of Marriage: and the Two Shall Remain Two" presented on Oct 14, 2006 at the Southeastern Undergraduate Philosophy Conference at UNCA, Asheville, NC

[1] ``The Humanist Lemma: A Means of Discourse" presented February of 2006 at the Annual Meeting of the North Carolina Philosophical Society, Columbia, SC

%---------------------------------------------------------------------------

\section{\bf Publicly Available Software Packages}

[3] VerbalVictor, an iPad and iPhone application that allows speech impared individuals to communicate using fully customizable recordings.  This project was featured in the LATimes, Chicago Tribune, as well as other leading papers.

[2] SNPLASH.  Designed as a comprehensive set of utilities for genome wide association study analysis.  Includes the ability to consider single locus association with a quantitative or binary decision variable, full linkage disequilibrium and haplotype approximation using the EM algorithm, a test for interaction between 2 markers using a binary trait, and support for the Bagged ADTrees algorithm.  Major language: C++. Available at \tt{http://www.github.org/guyrt} 

[1] SNPdoc: A Web Based SNP selection utility.  Aggregates useful biological and statistical information to aid in SNP selection in genome wide association studies.  Web access available at (https://wakegen.phs.wfubmc.edu/public/snpdoc/index.cfm).  Download access available at \\ (http://www.phs.wfubmc.edu/public/bios/gene/downloads.cfm).  Major languages: Perl, SQL. Utilizes publicly available data access APIs from the UCSC Genome Project, NCBI, and Ensembl.

\section{\bf Service}

\begin{itemize}
\item Organized and taught a 2-week workshop called the Advanced School for Scientific Developement at the International Center for Theoretical Physics, Trieste, Italy. February, 2012.
\item Organized and taught Software Carpentry 2-day workshop in Toronto, Ontario, November 2011.
\item Co-leader of the graduate student visit day at the University of Toronto, March 2011. 
\item At Large Member (Leadership position) in the Computer Science Graduate Student Benevolent Society (CSGSBS), Dept. of Computer Science, University of Toronto.
\item Chair of session ``Contributed Papers in Difference and Functional Equations" at JMM 2009, Washington D.C.
\item Chair of session ``Contributed Papers in Difference and Functional Equations" at JMM 2009, Washington D.C.
\item Graduate President, Pi Mu Epsilon, Wake Forest University, 2008-2009
\item Senator, Student Government Association, Appalachian State University, 2005-2006
\end{itemize}

%%---------------------------------------------------------------------------%%



%%---------------------------------------------------------------------------%%

\section{\bf Academic Organizations}

\begin{itemize}
\item Association for Computing Machinery
\item International Society for Difference Equations (Sponsoring member)
\item American Mathematical Society
\item Society for Industrial and Applied Mathematics
\end{itemize}

%\section{\bf Computing Languages and Platforms }

%Fluent: C, C++, Perl, Matlab, \LaTeX, SQL, BASH, HTML

%Competent:  Java, R, Maple, ObjC

%Familiar: SAS, CSS, XML

\end{resume}

\end{document}

%%===========================================================================%%
